Run AwAI: StarCraftII Adversary Avoidance Using Neural Networks and Genetic Algorithms

### 2018-06-06 doc/run_awai.tex

  This project explores the integration of a neural network and an evolutionary
  genetic algorithm with the Star Craft II API.The goal of this project was to
  successfully control a StarCraft II agent via a neural network, and maximize
  its fitness through a genetic evolutionary algorithm. The agent uses the PySC2
  API to connect with StarCraft II, and a neural network to control its
  actions.The fitness function is defined as the survival duration for an agent
  in a sandbox environment with hostile units, where surviving for longer is
  better.The action space of the agent was limited to movement in order to
  achieve a realistic scope for the project.The fitness of an individual is
  evaluated by running multiple simulation episodes and averaging the
  performance (survival time) for each episode.The neural network uses an
  explicit topologically unrestricted implementation.This implementation
  provides high degrees of freedom while minimizing the network size.The genetic
  algorithm uses tournament selection to select the most fit neural network
  (individuals) to breed.Each successive generation of neural networks is
  slightly better at surviving in the hostile sandbox environment.After 50
  iterative generations, our resulting neural network had increased the average
  survival time of an agent by 288%.

@@

\begin{figure}[h]\label{fig:flow chart}
\centering
\includegraphics[width=0.45\textwidth]{chart}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Control and data flow through the Run AwAI controller.}
\end{changemargin}
\end{figure}

@@

\begin{figure}[h]\label{fig:fitness graph}
\centering
\includegraphics[width=0.45\textwidth]{fig_1}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Graph of average fitness (blue) and top fitness (orange) for each
    generation in Trial 1. Top fitness is the fitness of the most fit individual
    at the end of each generation's simulations. Average fitness is calculated
    by averaging \eqref{eq:fitness} over all individuals $\bm{i}$ in the
    population. The breeding constant is set to 15, node generation rate is set
    to 0.3, new connections at 0.2 and non structural mutations at a rate of
    0.4}
\end{changemargin}
\end{figure}

@@

\begin{figure}[h]\label{fig:fitness graph}
\centering
\includegraphics[width=0.45\textwidth]{fig_2}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Graph of average fitness (blue) and top fitness (orange) for each
    generation in Trial 1. Top fitness is the fitness of the most fit individual
    at the end of each generation's simulations. Average fitness is calculated
    by averaging \eqref{eq:fitness} over all individuals $\bm{i}$ in the
    population. The breeding constant is set to 15, node generation rate is set
    to 0.5, new connections at 0.5 and non structural mutations at a rate of
    0.75}
\end{changemargin}
\end{figure}

>>>>

  This project explores the integration of a neural network and an evolutionary
  genetic algorithm with the Star Craft II API. The goal of this project was to
  successfully control a StarCraft II agent via a neural network, and maximize
  its fitness through a genetic evolutionary algorithm. The agent uses the PySC2
  API to connect with StarCraft II, and a neural network to control its
  actions. The fitness function is defined as the survival duration for an agent
  in a sandbox environment with hostile units, where surviving for longer is
  better. The action space of the agent was limited to movement in order to
  achieve a realistic scope for the project. The fitness of an individual is
  evaluated by running multiple simulation episodes and averaging the
  performance (survival time) for each episode. The neural network uses an
  explicit topologically unrestricted implementation. This implementation
  provides high degrees of freedom while minimizing the network size. The genetic
  algorithm uses tournament selection to select the most fit neural network
  (individuals) to breed. Each successive generation of neural networks is
  slightly better at surviving in the hostile sandbox environment. After 50
  iterative generations, our resulting neural network had increased the average
  survival time of an agent by 288\%.

@@

\begin{figure}[h]\label{fig:flow chart}
\centering
\includegraphics[width=0.75\textwidth]{chart}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Control and data flow through the Run AwAI controller.}
\end{changemargin}
\end{figure}

@@

\begin{figure}[h]\label{fig:fitness graph}
\centering
\includegraphics[width=0.75\textwidth]{fig_1}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Graph of average fitness (blue) and top fitness (orange) for each
    generation in Trial 1. Top fitness is the fitness of the most fit individual
    at the end of each generation's simulations. Average fitness is calculated
    by averaging \eqref{eq:fitness} over all individuals $\bm{i}$ in the
    population. The breeding constant is set to 15, node generation rate is set
    to 0.3, new connections at 0.2 and non structural mutations at a rate of
    0.4}
\end{changemargin}
\end{figure}

@@

\begin{figure}[h]\label{fig:fitness graph}
\centering
\includegraphics[width=0.75\textwidth]{fig_2}
\begin{changemargin}{0.15in}{0.15in}
  \caption{Graph of average fitness (blue) and top fitness (orange) for each
    generation in Trial 1. Top fitness is the fitness of the most fit individual
    at the end of each generation's simulations. Average fitness is calculated
    by averaging \eqref{eq:fitness} over all individuals $\bm{i}$ in the
    population. The breeding constant is set to 15, node generation rate is set
    to 0.5, new connections at 0.5 and non structural mutations at a rate of
    0.75}
\end{changemargin}
\end{figure}
